A deeper look into bug fixes: Patterns, replacements, deletions, and additions

### 2016-02-19 MSRChallenge2016.tex
intro, related work

\maketitle
\begin{abstract}
  Many implementations of recent work to automatically repair bugs in software
  target programs written in C. Work that targets Java often begins from, or at
  least compares to, direct translations of such techniques to a Java context.
  However, Java and C are very different languages, and these differences should be
  studied and understood if existing approaches are to be profitably translated
  from one to another.  We conducted a large-scale study of bug-fixing commits
  to Java projects, focusing on assumptions underlying common
  search-based repair approaches.  We make a number of observations that can be
  leveraged to guide automatic software repair to target Java specifically,
  including common and uncommon statement replacements as conducted by human
  developers and the applicability of previously-proposed patch construction
  operators in the Java context.  We anticipate that these observations can
  inform more effective patch construction techniques for Java, both in raw
  numbers of bugs fixed and the usability and maintainability of the resulting
  patches. 
\end{abstract}

@@

Research in automatic bug repair seeks to develop techniques that can
automatically construct patches to repair software bugs, which are prevalent in
practice. There has been considerable attention paid to this problem in recent
years~\cite{kim2013,weimer2009,legoues2012,pan2009,so,many,more}.
Mutation-based, or generate-and-validate approaches, typically operate by
generating a large number of candidate patches using a pre-defined set of
mutation operators, and then validating their correctness with respect to a set
of test cases.  These mutation operators range from simple, coarse granularity
statement-level mutations~\cite{examples} to human-constructed templates learned
from a large corpus of previous human bug-fixing commits~\cite{kim2013}.

A considerable proportion of this previous work is implemented to target
programs written in C, with only limited attention paid to programs in other
languages, like Java~\cite{kim2013}.  At least partially as a result,
researchers targeting Java must either start from or at least compare against
imperfect baselines, that is, Java-based implementations of techniques
originally implemented for C~\cite{nopol}. %  Even PAR~\cite{kim2013}, perhaps the
% best-known previously-proposed Java-based program repair technique, both starts
% from and is directly compared to a Java implementation of GenProg~\cite{genprog}, which
% targets the C programming language.  
This C focus extends to empirical studies
of bug fixing practice, used to inform research questions in automatic
repair~\cite{zhong2015}.

This is an oversight, because, to put it simply: Java and C are very different
languages.  Consider GenProg~\cite{genprog,cites}, a well-known technique in
this space: GenProg uses a genetic programming heuristic to combine
statement-level mutations into patches to address a particular defect.
``Statement'' is a well-defined semantic unit in the C programming
language~\cite{cspec}; to which semantic unit in Java does this concept map?
Can we learn more
intelligent rules to inform candidate modifications
(cf. Prophet~\cite{rinardPopl2016}, for C)?  What types of
semantic scoping rules should be used to limit mutations, given the relative
stringence of the Java compilers?

In this paper, we study bug-fixing commits to Java programs, taking as a subject
of study several million human-made bug fixes from Github. We study broad
characteristics of changes to fix bugs; the applicability of previously-proposed
templates to repairing defects in Java programs~\cite{kim2013}; and the nature
of additions, replacements, of statements in bug-fixing commits. We make
observations to directly guide future research in automatic repair to Java
programs, to increase the success rate of such techniques and the degree to
which the patches are human-like and therefore more readable and maintainable by
human developers; this is important, because patch quality is an important
concern in this research area~\cite{Qi2013}.

@@

A good complement for this paper is~\cite{zhong2015}, where they look for
additions and deletions in a smaller data set. In this paper, we focus more on
the replacements, which have been left out of the analysis of~\cite{zhong2015},
and expand their results of the deletions and additions in a broader
dataset~\cite{dyer2013}.
\todo{note to self (CLG) should mention the work from Earl, Yuriy, and others
  that looked at the redundancy assumption.}

\todo{roadmap}

>>>>

\maketitle
\begin{abstract}
  Many implementations of research techniques that automatically repair software
  bugs target programs written in C. Work that targets Java often begins from, or at
  least compares to, direct translations of such techniques to a Java context.
  However, Java and C are very different languages, and these differences should be
  studied and understood if existing approaches are to be profitably translated
  between them.  We conducted a large-scale study of bug-fixing commits
  to Java projects, focusing on assumptions underlying common
  search-based repair approaches.  We make observations that can be
  leveraged to guide high quality automatic software repair to target Java specifically,
  including common and uncommon statement replacements as conducted by human
  developers and the applicability of previously-proposed patch construction
  operators in the Java context. 
\end{abstract}

@@

There has been considerable attention paid to the problem of automatic
program repair in recent
years~\cite{kim2013,legoues2012,pan2009,Weimer13, Qi13,
  Mechtaev15,prophet}, among many others),
%
One broad class of techniques in this space take a generate-and-validate
approach, which involves generating a large number of candidate patches using a
pre-defined set of mutation operators, and then validating correctness with
respect to a set of test cases.  Mutation operators range from simple, coarse
granularity statement-level mutations to human-constructed templates learned
from a large corpus of previous human bug-fixing commits.

A considerable proportion of this works targets programs written in C.
Researchers targeting Java often start from or compare against imperfect
baselines, that is, Java-based implementations of techniques originally
implemented for C~\cite{nopol,kim2013}. % Even PAR~\cite{kim2013}, perhaps the
% best-known previously-proposed Java-based program repair technique, both starts
% from and is directly compared to a Java implementation of GenProg~\cite{genprog}, which
% targets the C programming language.  
%
This is an oversight, because, frankly Java and C are very different languages.
Consider GenProg~\cite{legoues2012}, which
combines statement-level mutations into patches to address a particular
defect. Which ``Statements'' (a semantic unit in C) should be manipulated in Java?
Can we learn
intelligent rules to inform candidate modifications
(cf. Prophet~\cite{Long2016}, for C)?  What types of semantic scoping
should limit mutations, given the relative stringence of the Java
compiler?

In this paper, we study bug-fixing commits to Java programs, taking as a subject
of study several million human-made bug fixes from Github. We study broad
characteristics of these changes; the applicability of previously-proposed
Java repair templates~\cite{kim2013}; and the nature
of additions and replacements of Java statements in bug-fixing commits. We make
observations to directly guide future research in automatic repair of Java
programs, to increase the success rate of such techniques and the degree to
which the patches are human-like and therefore more readable and maintainable by
human developers. This is important, because patch quality is an important
concern in this research area~\cite{Qi15}.

@@

\noindent\textbf{Related work.} A good complement to this paper is~\cite{zhong2015}, which studies 
a similar set of questions in C.  Beyond focusing on Java, we focus more on
replacements, ommitted from that previous analysis, and otherwise target a
larger dataset~\cite{dyer2013}.  Barr et al.~\cite{Barr14fse} studied changes to
Java programs to understand the ``Plastic Surgery Hypothesis'' underlying
certain types of program repair techniques, an important but orthogonal
concern. Kim et al.~\cite{kim2013} manually analyze 
changes to Java programs to inform an automated repair
technique and show that doing so results in higher-quality repairs; 
we attempt to validate their learned templates heuristically on
a different dataset, and take their results as
motivation for understanding human repairs (as it may result in better patches).
Long and Rinard learn probabilistic models from bug fixes to C
code~\cite{Long2016}. Our analysis is significantly less precise and does not
inform a new repair technique.  Rather, it serves as a starting
point for research investigating the repair of bugs in Java code.
